Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-02-01 Master Thesis/synopsis.tex
Add some references

\begin{lemma}\label{spv-topology}
$\operatorname{Spv}(K)$ with the topology defined above is a quasicompact $T_0$-space. Every closed subset $A\subset\operatorname{Spv}(K)$ is the closure of its closed points.

In particular the set of closed points $|\operatorname{Spv}(K)|$ of $\operatorname{Spv}(K)$ is a quasicompact $T_1$-space, endowed with the induced topology. 
\end{lemma}

\begin{proof}
See [ZS] VI §7 Theorem 40.
\end{proof}

\begin{lemma}\label{2.2-pre}
Let $v,w\in\operatorname{Spv}(K)$. We have:
\[\mathcal{O}_w\subset\mathcal{O}_v \iff w\in\overline{\{v\}} \]
Thus $v$ is a closed point if and only if it has no non-trivial specializations. Furthermore, for a fixed $v\in \operatorname{Spv}(K)$ there is a canonical bijection: 
\begin{align*}
\{ w\in\operatorname{Spv}(K)\mid \mathcal{O}_w\subset\mathcal{O}_v \} &\longrightarrow \operatorname{Spv}k(v)\\ 
w&\longmapsto w\mod v
\end{align*}
Therefore $v$ is a closed point iff $k(v)$ only admits the trivial valuation, i.e. $k(v)$ has positive characteristic $p>0$ and is algebraic over $\mathbb{F}_p$. In other words, $v$ is a closed point iff $\dim k(v)=0$. By the dimension inequality \ref{rank-dimension-inequality} we have $\operatorname{Spv}^{(n)}(K)\subset |\operatorname{Spv}(K)|$ where $n=\dim(K)$.

@@

\begin{proof}
See Valued Fields 4.1.4.
\end{proof}

@@

>>>>

\begin{lemma}\label{spv-topology}
$\operatorname{Spv}(K)$ with the topology defined above is a quasicompact $T_0$-space. In particular the set of closed points $|\operatorname{Spv}(K)|$ of $\operatorname{Spv}(K)$ is a quasicompact $T_1$-space, endowed with the induced topology. Let $v,w\in\operatorname{Spv}(K)$. We have:
\[\mathcal{O}_w\subset\mathcal{O}_v \iff w\in\overline{\{v\}} \]
Thus $v$ is a closed point if and only if it has no non-trivial specializations.
\end{lemma}

\begin{proof}
See [ZS] VI §17 Theorem 38, §17 Theorem 40.
\end{proof}

\begin{lemma}\label{2.2-pre}
For a fixed $v\in \operatorname{Spv}(K)$ there is a canonical bijection: 
\begin{align*}
\{ w\in\operatorname{Spv}(K)\mid \mathcal{O}_w\subset\mathcal{O}_v \} &\longrightarrow \operatorname{Spv}k(v)\\ 
w&\longmapsto w\mod v
\end{align*}
Therefore $v$ is a closed point iff $k(v)$ only admits the trivial valuation, i.e. $k(v)$ has characteristic $p>0$ and is algebraic over $\mathbb{F}_p$. In other words, $v$ is a closed point iff $\dim k(v)=0$. By the dimension inequality \ref{rank-dimension-inequality} we have $\operatorname{Spv}^{(n)}(K)\subset |\operatorname{Spv}(K)|$ where $n=\dim(K)$.

@@

\begin{proof}
See Valued Fields 4.1.4, [ZS] VI §3 Theorem 3.
\end{proof}

@@

\begin{proof}
See [ZS] VI §10 Theorem 18
\end{proof}
